Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-01-31 ms.tex
added plot with apertres in subarray config test.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.5\columnwidth]{subarray_config_tser_backsub_rect.pdf}
\caption{With rect backub.
\textcolor{red}{To do: understand better why the vertically offset box is better? Also, show the aperture as a separate figure.}}\label{fig:OTISRectBacksub}
\end{figure}

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=0.48\columnwidth]{apertures_for_NRCN83-128-STRIPE-72.pdf}
\includegraphics[width=0.48\columnwidth]{apertures_for_NRCN83-256-STRIPE-72.pdf}
\includegraphics[width=.48\columnwidth]{subarray_config_tser_backsub_rect.pdf}
\caption{With rect backub.
\textcolor{red}{To do: understand better why the vertically offset box is better? Also, show the aperture as a separate figure.}}\label{fig:OTISRectBacksub}
\end{figure}
